Manuscript results: Forecasting influenza using ARIMA and ARIMAX

### 2025-05-06 manuscript_results.Rmd
update

# Plotting forecasts and ribbon
plt00 <- ggplot(forecast_df, aes(x = Week, y = Value, group = 1)) +
  geom_line(color = "black", size = 1) +          # Line connecting forecast values
  geom_point(color = "black", size = 3) +         # Points for each forecast value
  geom_ribbon(aes(ymin = Lower, ymax = Upper),   # Ribbon for confidence intervals
              fill = "gray", alpha = 0.25) +
  labs(title = "Example of influenza hospitalizaions forecasts with 95% confidence intervals",
       x = "Target Weeks",
       y = "Forecast Values") +
  theme_minimal()

@@

ggsave(plt00, height = 5, width = 6, filename="fig00.jpg") 
```

@@

# Plot
plt0 <- ggplot(df_combined_, aes(x = Julian_date, y = WIS, group = STATE)) + 
  geom_vline(data = highlight_dates, aes(xintercept = Julian_date), color = "red", linetype = "dashed", size = 1) +  
  geom_line(color = "black", size = 0.2) +  
  facet_wrap(~ Dataset, ncol = 2, scales = "free_y") +  
  theme_minimal() +  
  labs(title = "Baseline Model WIS for 48 states on the contiguous U.S.",#,
#       subtitle = "Dashed red lines indicates epidemiological weeks outsise of the influenza season",
       x = "Month", 
       y = "WIS") +  
  theme(axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.position = "none") + 
  scale_x_date(labels = scales::date_format("%b"), breaks = "2 month")  # Format x-axis to show months and set monthly breaks

@@

ggsave(plt0, height = 5, width = 6, filename="fig0.jpg")  
```

@@

# Create the plot
combined_plot <- ggplot(all_weeks, aes(x = Best_Result, fill = Best_Result)) +
  geom_bar() +
  scale_fill_manual(values = custom_colors) +
  labs(title = "Best model based on the lowest mean WIS on 48 U.S. states",
       x = "", y = "Number of states") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_grid(Week_Ahead ~ Model_Type, scales = "free_x")

# Save and display the plot
ggsave("Fig2.jpg", combined_plot, width = 10, height = 8)
print(combined_plot)

@@

    ES27_AR = ((1 - (data$ES27_AR/data$AUTO_AR)) * 100),
    ES64_AR = ((1 - (data$ES64_AR/data$AUTO_AR )) * 100),

    AUTO_ADJ = ((1 - (data$AUTO_ADJ/data$AUTO_AR)) * 100),
    ES27_ADJ = ((1 - (data$ES27_ADJ/data$AUTO_AR)) * 100),
    ES64_ADJ = ((1 - (data$ES64_ADJ/data$AUTO_AR)) * 100),

    AUTO_TMP = ((1 - (data$AUTO_TMP/data$AUTO_AR)) * 100),
    ES27_TMP = ((1 - (data$ES27_TMP/data$AUTO_AR)) * 100),
    ES64_TMP = ((1 - (data$ES64_TMP/data$AUTO_AR)) * 100),

    AUTO_EPI = ((1 - (data$AUTO_EPI/data$AUTO_AR)) * 100),
    ES27_EPI = ((1 - (data$ES27_EPI/data$AUTO_AR)) * 100),
    ES64_EPI = ((1 - (data$ES64_EPI/data$AUTO_AR)) * 100),

    AUTO_AVG = ((1 - (data$AUTO_AVG/data$AUTO_AR)) * 100),
    ES27_AVG = ((1 - (data$ES27_AVG/data$AUTO_AR)) * 100),
    ES64_AVG = ((1 - (data$ES64_AVG/data$AUTO_AR)) * 100),

    AUTO_AR_LB = ((1 - (data$AUTO_AR_LB/data$AUTO_AR)) * 100),
    ES27_AR_LB = ((1 - (data$ES27_AR_LB/data$AUTO_AR)) * 100),
    ES64_AR_LB = ((1 - (data$ES64_AR_LB/data$AUTO_AR)) * 100),

    AUTO_ADJ_LB = ((1 - (data$AUTO_ADJ_LB/data$AUTO_AR)) * 100),
    ES27_ADJ_LB = ((1 - (data$ES27_ADJ_LB/data$AUTO_AR)) * 100),
    ES64_ADJ_LB = ((1 - (data$ES64_ADJ_LB/data$AUTO_AR)) * 100),

    AUTO_TMP_LB = ((1 - (data$AUTO_TMP_LB/data$AUTO_AR)) * 100),
    ES27_TMP_LB = ((1 - (data$ES27_TMP_LB/data$AUTO_AR)) * 100),
    ES64_TMP_LB = ((1 - (data$ES64_TMP_LB/data$AUTO_AR)) * 100),

    AUTO_EPI_LB = ((1 - (data$AUTO_EPI_LB/data$AUTO_AR)) * 100),
    ES27_EPI_LB = ((1 - (data$ES27_EPI_LB/data$AUTO_AR)) * 100),
    ES64_EPI_LB = ((1 - (data$ES64_EPI_LB/data$AUTO_AR)) * 100),

    AUTO_AVG_LB = ((1 - (data$AUTO_AVG_LB/data$AUTO_AR)) * 100),
    ES27_AVG_LB = ((1 - (data$ES27_AVG_LB/data$AUTO_AR)) * 100),
    ES64_AVG_LB = ((1 - (data$ES64_AVG_LB/data$AUTO_AR)) * 100)    
  ))
}

@@

# Heatmap plot with models ordered by WeekAhead == 1  
plot_m_heatmap <- ggplot(p_df, aes(x = factor(WeekAhead), y = Model, fill = m)) +
  geom_tile(aes(fill = ifelse(Significance == "Significant", m, NA)), color = "black") +  # Fill only significant ones
  geom_tile(data = p_df %>% filter(Significance == "Not Significant"), 
            aes(x = factor(WeekAhead), y = Model), fill = "gray80", color = "black") +  # Gray for non-significant
  geom_text(aes(label = paste0("m:", round(m, 2),", sd:", round(sd, 2))), 
            color = "black", size = 4) +  # Add text labels
  scale_fill_gradient(low = "red", high = "cyan", na.value = "gray80", 
                      name = "Percentage (%)", limits = c(-35, 35)) +  # Fixed color scale from -30 to 30
  labs(title = "Figure X:Mean differences between models' WIS and the baseline across 48 states",
       subtitle = "Gray boxes indicate models that are not significantly different from the baseline (p>0.05)",
         caption = "m = mean difference, sd = standard deviation",
       x = "Week Ahead",
       y = "") + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
  plot.caption = element_text(size = 12),
    plot.title = element_text(size = 18, face = "bold"),
    plot.subtitle = element_text(size = 14),) +
  facet_wrap(~ Model_Type, scales = "free_y")  # Separate NoLg and other models

@@

```{r}
# Assuming merged_data already includes the necessary columns: model and percentage_improveme
# Create the map plot for 1 Week Ahead with best models and percentage improvement
ES_1WEEK <- ggplot(W1_map) +
  geom_sf(aes(fill = percentage_improvement)) +  # Fill based on the best model
  scale_fill_gradient2(low = "darkred", mid = "lightyellow", high = "skyblue", midpoint = 0, limits = c(-30, 60)) +  
  ggtitle("Mean WIS improvement in percentage (W1)") +
  theme_light() +
  theme(legend.position = "right") +
  geom_sf_text(data = W1_map, aes(label = round(percentage_improvement,1)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE) +  # Display percentage improvement in each state
  labs(
    fill = "%",  # Label for the legend
    subtitle = "(1-(Baseline/AUTO_AVG_LB))*100"
            , 
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ggsave(ES_1WEEK,height = 4.5, width = 6.5,  filename="Fig5A.jpg")  
```
2 weeks ahead

@@

# Assuming merged_data already includes the necessary columns: model and percentage_improveme
# Create the map plot for 1 Week Ahead with best models and percentage improvement
ES_2WEEK <- ggplot(W2_map) +
  geom_sf(aes(fill = percentage_improvement)) +  # Fill based on the best model
  scale_fill_gradient2(low = "darkred", mid = "lightyellow", high = "skyblue", midpoint = 0, limits = c(-30, 60)) +  
  ggtitle("Mean WIS improvement in percentage (W2)") +
  theme_light() +
  theme(legend.position = "right") +
  geom_sf_text(data = W2_map, aes(label = round(percentage_improvement,1)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE) +  # Display percentage improvement in each state
  labs(
    fill = "%",  # Label for the legend
    subtitle = "(1-(Baseline/AUTO_AVG_LB))*100"
            , 
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ggsave(ES_2WEEK, height = 4.5, width = 6.5, filename="Fig5B.jpg")  
```

@@

ES_3WEEK <- ggplot(W3_map) +
  geom_sf(aes(fill = percentage_improvement)) +  # Fill based on the best model
  scale_fill_gradient2(low = "darkred", mid = "lightyellow", high = "skyblue", midpoint = 0, limits = c(-30, 60)) +  
  ggtitle("Mean WIS improvement in percentage (W3)") +
  theme_light() +
  theme(legend.position = "right") +
  geom_sf_text(data = W3_map, aes(label = round(percentage_improvement,1)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE) +  # Display percentage improvement in each state
  labs(
    fill = "%",  # Label for the legend
    subtitle = "(1-(Baseline/AUTO_AVG_LB))*100"
            , 
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ggsave(ES_3WEEK, height = 4.5, width = 6.5, filename="Fig5C.jpg")  
```
4 weeks ahead

@@

ES_4WEEK <- ggplot(W4_map) +
  geom_sf(aes(fill = percentage_improvement)) +  # Fill based on the best model
  scale_fill_gradient2(low = "darkred", mid = "lightyellow", high = "skyblue", midpoint = 0, limits = c(-30, 60)) +  
  ggtitle("Mean WIS improvement in percentage (W4)") +
  theme_light() +
  theme(legend.position = "right") +
  geom_sf_text(data = W4_map, aes(label = round(percentage_improvement,1)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE) +  # Display percentage improvement in each state
  labs(
    fill = "%",  # Label for the legend
    subtitle = "(1-(Baseline/AUTO_AVG_LB))*100"
            , 
       x = "",
       y = ""
  )  # Adding a subtitle

@@

ggsave(ES_4WEEK, height = 4.5, width = 6.5,  filename="Fig5D.jpg")  
```
REGRESSION MODELS

@@

  # Sum values by Julian date across all states
  summed_data <- data__ %>%
    group_by(Julian_date) %>%
    summarize(
      AUTO_AR = sum(AUTO_AR, na.rm = TRUE),  # Sum across all states
      AUTO_AVG_LB = sum(AUTO_AVG_LB, na.rm = TRUE)           # Sum across all states
    ) %>%
    # Calculate the difference ratio
    mutate(Difference = 1 - (AUTO_AVG_LB / AUTO_AR),
           Week = paste0("Week ", week))

@@

# Plot the difference using ggplot2
model_improv<-ggplot(summed_data_all, aes(x = Julian_date, y = (Difference)*100, color = Week)) +
  geom_point(size = 3) +
  geom_hline(yintercept = 0, color = "black", linetype = "dashed", size = 0.8) +
  theme_minimal() +
  labs(
    title = "Figure X: Mean percentage of WIS differences across all states",
    subtitle = "AUTO_AVG_LB compared to baseline",
    x = "",
    y = "Difference (%)"
  ) +
  scale_y_continuous(
    limits = c(-100, 100),
    breaks = seq(-100, 100, by = 20)
  ) +
  scale_x_date(
    date_breaks = "1 month",
    date_labels = "%b %y"
  ) +
  scale_color_manual(
    values = c("Week 1" = "#ffcccc",
               "Week 2" = "#ff6666",
               "Week 3" = "#cc0000",
               "Week 4" = "#990000")
  ) +
  theme(
    plot.title = element_text(size = 18, face = "bold"),
    plot.subtitle = element_text(size = 14),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

>>>>

# Plotting forecasts and ribbon
plt00 <- ggplot(forecast_df, aes(x = Week, y = Value, group = 1)) +
  geom_line(color = "black", size = 1) +          # Line connecting forecast values
  geom_point(color = "black", size = 3) +         # Points for each forecast value
  geom_ribbon(aes(ymin = Lower, ymax = Upper),   # Ribbon for confidence intervals
              fill = "gray", alpha = 0.25) +
  labs(title = "Figure X: Example of influenza hospitalizaions forecasts",
       subtitle = "The gray ribbon indicates the 95% confidence interval",
       x = "Target Weeks",
       y = "Forecast Values") +
  theme_minimal() +
  theme(plot.title = element_text(size = 16, face = "bold"),
        plot.subtitle = element_text(size = 14))

@@

ggsave(plt00, height = 5, width = 10, filename="fig00.jpg") 
```

@@

# Plot
plt0 <- ggplot(df_combined_, aes(x = Julian_date, y = WIS, group = STATE)) + 
  geom_vline(data = highlight_dates, aes(xintercept = Julian_date), color = "red", linetype = "dashed", size = 1) +  
  geom_line(color = "black", size = 0.2) +  
  facet_wrap(~ Dataset, ncol = 2, scales = "free_y") +  
  theme_minimal() +  
  labs(title = "Figure X: Baseline model WIS for 48 states on the contiguous U.S.",#,
#       subtitle = "Dashed red lines indicates epidemiological weeks outsise of the influenza season",
       x = "Month", 
       y = "WIS") +  
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(size = 16, face = "bold"),
        legend.position = "none") + 
  scale_x_date(labels = scales::date_format("%b"), breaks = "2 month")  # Format x-axis to show months and set monthly breaks

@@

ggsave(plt0, height = 5, width = 8, filename="fig0.jpg")  
```

@@

# Create the plot
combined_plot <- ggplot(all_weeks, aes(x = Best_Result, fill = Best_Result)) +
  geom_bar() +
  scale_fill_manual(values = custom_colors) +
  labs(title = "Figure X: Best model based on the lowest mean WIS",
       subtitle = "Across the 48 states on the contiguous U.S.",
       x = "", y = "Number of states",
       fill = "Best model" ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(size = 16, face = "bold")) +
  facet_grid(Week_Ahead ~ Model_Type, scales = "free_x")

# Save and display the plot
ggsave("Fig2.jpg", combined_plot, width =8, height =5)
print(combined_plot)

@@

    ES27_AR = (-(1 - (data$ES27_AR/data$AUTO_AR)) * 100),
    ES64_AR = (-(1 - (data$ES64_AR/data$AUTO_AR )) * 100),

    AUTO_ADJ = (-(1 - (data$AUTO_ADJ/data$AUTO_AR)) * 100),
    ES27_ADJ = (-(1 - (data$ES27_ADJ/data$AUTO_AR)) * 100),
    ES64_ADJ = (-(1 - (data$ES64_ADJ/data$AUTO_AR)) * 100),

    AUTO_TMP = (-(1 - (data$AUTO_TMP/data$AUTO_AR)) * 100),
    ES27_TMP = (-(1 - (data$ES27_TMP/data$AUTO_AR)) * 100),
    ES64_TMP = (-(1 - (data$ES64_TMP/data$AUTO_AR)) * 100),

    AUTO_EPI = (-(1 - (data$AUTO_EPI/data$AUTO_AR)) * 100),
    ES27_EPI = (-(1 - (data$ES27_EPI/data$AUTO_AR)) * 100),
    ES64_EPI = (-(1 - (data$ES64_EPI/data$AUTO_AR)) * 100),

    AUTO_AVG = (-(1 - (data$AUTO_AVG/data$AUTO_AR)) * 100),
    ES27_AVG = (-(1 - (data$ES27_AVG/data$AUTO_AR)) * 100),
    ES64_AVG = (-(1 - (data$ES64_AVG/data$AUTO_AR)) * 100),

    AUTO_AR_LB = (-(1 - (data$AUTO_AR_LB/data$AUTO_AR)) * 100),
    ES27_AR_LB = (-(1 - (data$ES27_AR_LB/data$AUTO_AR)) * 100),
    ES64_AR_LB = (-(1 - (data$ES64_AR_LB/data$AUTO_AR)) * 100),

    AUTO_ADJ_LB = (-(1 - (data$AUTO_ADJ_LB/data$AUTO_AR)) * 100),
    ES27_ADJ_LB = (-(1 - (data$ES27_ADJ_LB/data$AUTO_AR)) * 100),
    ES64_ADJ_LB = (-(1 - (data$ES64_ADJ_LB/data$AUTO_AR)) * 100),

    AUTO_TMP_LB = (-(1 - (data$AUTO_TMP_LB/data$AUTO_AR)) * 100),
    ES27_TMP_LB = (-(1 - (data$ES27_TMP_LB/data$AUTO_AR)) * 100),
    ES64_TMP_LB = (-(1 - (data$ES64_TMP_LB/data$AUTO_AR)) * 100),

    AUTO_EPI_LB = (-(1 - (data$AUTO_EPI_LB/data$AUTO_AR)) * 100),
    ES27_EPI_LB = (-(1 - (data$ES27_EPI_LB/data$AUTO_AR)) * 100),
    ES64_EPI_LB = (-(1 - (data$ES64_EPI_LB/data$AUTO_AR)) * 100),

    AUTO_AVG_LB = (-(1 - (data$AUTO_AVG_LB/data$AUTO_AR)) * 100),
    ES27_AVG_LB = (-(1 - (data$ES27_AVG_LB/data$AUTO_AR)) * 100),
    ES64_AVG_LB = (-(1 - (data$ES64_AVG_LB/data$AUTO_AR)) * 100)    
  ))
}

@@

# Heatmap plot with models ordered by WeekAhead == 1  
plot_m_heatmap <- ggplot(p_df, aes(x = factor(WeekAhead), y = Model, fill = m)) +
  geom_tile(aes(fill = ifelse(Significance == "Significant", m, NA)), color = "black") +  # Fill only significant ones
  geom_tile(data = p_df %>% filter(Significance == "Not Significant"), 
            aes(x = factor(WeekAhead), y = Model), fill = "gray80", color = "black") +  # Gray for non-significant
  geom_text(aes(label = paste0("m:", round(m, 2),", sd:", round(sd, 2))), 
            color = "black", size = 4) +  # Add text labels
  scale_fill_gradient(low = "cyan", high = "red", na.value = "gray80", 
                      name = "Percentage (%)", limits = c(-35, 35)) +  # Fixed color scale from -30 to 30
  labs(title = "Figure X: Mean differences between models' WIS and the baseline across 48 states",
       subtitle = "Gray boxes indicate models that are not significantly different from the baseline (p>0.05)",
         caption = "m = mean difference (%), sd = standard deviation",
       x = "Week Ahead",
       y = "") + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
  plot.caption = element_text(size = 12),
    plot.title = element_text(size = 18, face = "bold"),
    plot.subtitle = element_text(size = 14),) +
  facet_wrap(~ Model_Type, scales = "free_y")  # Separate NoLg and other models

@@

```{r}
# Assuming merged_data already includes the necessary columns: model and percentage_improveme
# Create the map plot for 1 Week Ahead with best models and percentage improvement
ES_1WEEK <- ggplot(W1_map) +
  geom_sf(aes(fill = percentage_improvement)) +  # Fill based on the best model
  scale_fill_gradient2(low ="skyblue" , mid = "lightyellow", high = "darkred", midpoint = 0, limits = c(-60, 30)) +  
  ggtitle("Mean WIS improvement in percentage (W1)") +
  theme_light() +
  theme(legend.position = "right") +
  geom_sf_text(data = W1_map, aes(label = round(percentage_improvement,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE) +  # Display percentage improvement in each state
  labs(
    fill = "%",  # Label for the legend
    subtitle = "(1-(Baseline/AUTO_AVG_LB))*100"
            , 
       x = "",
       y = ""
  )  # Adding a subtitle

@@

#ggsave(ES_1WEEK,height = 4.5, width = 6.5,  filename="Fig5A.jpg")  
```
2 weeks ahead

@@

# Assuming merged_data already includes the necessary columns: model and percentage_improveme
# Create the map plot for 1 Week Ahead with best models and percentage improvement
ES_2WEEK <- ggplot(W2_map) +
  geom_sf(aes(fill = percentage_improvement)) +  # Fill based on the best model
  scale_fill_gradient2(low ="skyblue" , mid = "lightyellow", high = "darkred", midpoint = 0, limits = c(-60, 30)) +  
  ggtitle("Mean WIS improvement in percentage (W2)") +
  theme_light() +
  theme(legend.position = "right") +
  geom_sf_text(data = W2_map, aes(label = round(percentage_improvement,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE) +  # Display percentage improvement in each state
  labs(
    fill = "%",  # Label for the legend
    subtitle = "(1-(Baseline/AUTO_AVG_LB))*100"
            , 
       x = "",
       y = ""
  )  # Adding a subtitle

@@

#ggsave(ES_2WEEK, height = 4.5, width = 6.5, filename="Fig5B.jpg")  
```

@@

ES_3WEEK <- ggplot(W3_map) +
  geom_sf(aes(fill = percentage_improvement)) +  # Fill based on the best model
  scale_fill_gradient2(low ="skyblue" , mid = "lightyellow", high = "darkred", midpoint = 0, limits = c(-60, 30)) +  
  ggtitle("Mean WIS improvement in percentage (W3)") +
  theme_light() +
  theme(legend.position = "right") +
  geom_sf_text(data = W3_map, aes(label = round(percentage_improvement,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE) +  # Display percentage improvement in each state
  labs(
    fill = "%",  # Label for the legend
    subtitle = "(1-(Baseline/AUTO_AVG_LB))*100"
            , 
       x = "",
       y = ""
  )  # Adding a subtitle

@@

#ggsave(ES_3WEEK, height = 4.5, width = 6.5, filename="Fig5C.jpg")  
```
4 weeks ahead

@@

ES_4WEEK <- ggplot(W4_map) +
  geom_sf(aes(fill = percentage_improvement)) +  # Fill based on the best model
  scale_fill_gradient2(low ="skyblue" , mid = "lightyellow", high = "darkred", midpoint = 0, limits = c(-60, 30)) +  
  ggtitle("Mean WIS improvement in percentage (W4)") +
  theme_light() +
  theme(legend.position = "right") +
  geom_sf_text(data = W4_map, aes(label = round(percentage_improvement,0)),  # Round to whole numbers
               size = 3,
               color = "black",
               check_overlap = TRUE) +  # Display percentage improvement in each state
  labs(
    fill = "%",  # Label for the legend
    subtitle = "(1-(Baseline/AUTO_AVG_LB))*100"
            , 
       x = "",
       y = ""
  )  # Adding a subtitle

@@

#ggsave(ES_4WEEK, height = 4.5, width = 6.5,  filename="Fig5D.jpg")  
```

library(patchwork)

# Ensure each plot has coord_sf applied
ES_1WEEK <- ES_1WEEK + coord_sf(xlim = x_limits, ylim = y_limits)
ES_2WEEK <- ES_2WEEK + coord_sf(xlim = x_limits, ylim = y_limits)
ES_3WEEK <- ES_3WEEK + coord_sf(xlim = x_limits, ylim = y_limits)
ES_4WEEK <- ES_4WEEK + coord_sf(xlim = x_limits, ylim = y_limits)

# Combine in a 2x2 grid
combined_plot <- (ES_1WEEK | ES_2WEEK) /
                 (ES_3WEEK | ES_4WEEK)

# Print
print(combined_plot)

# Save to file
ggsave("Fig5_2x2_combined.jpg", combined_plot, width = 15, height = 8)
```

@@

  # Sum values by Julian date across all states
  summed_data <- data__ %>%
    group_by(Julian_date) %>%
    summarize(
      AUTO_AR = sum(AUTO_AR, na.rm = TRUE),  # Sum across all states
      AUTO_AVG_LB = sum(AUTO_AVG_LB, na.rm = TRUE)           # Sum across all states
    ) %>%
    # Calculate the difference ratio
    mutate(Difference =  ((AUTO_AVG_LB / AUTO_AR)-1)*100,
           Week = paste0("Week ", week))

@@

# Plot the difference using ggplot2
model_improv<-ggplot(summed_data_all, aes(x = Julian_date, y = (Difference), color = Week)) +
  geom_point(size = 3) +
  geom_hline(yintercept = 0, color = "black", linetype = "dashed", size = 0.8) +
  theme_minimal() +
  labs(
    title = "Figure X: Mean percentage of WIS differences across all states",
    subtitle = "AUTO_AVG_LB compared to baseline",
    x = "",
    y = "Difference (%)"
  ) +
  scale_y_continuous(
    limits = c(-100, 100),
    breaks = seq(-100, 100, by = 20)
  ) +
  scale_x_date(
    date_breaks = "1 month",
    date_labels = "%b %y"
  ) +
  scale_color_manual(
    values = c("Week 1" = "#ffcccc",
               "Week 2" = "#ff6666",
               "Week 3" = "#cc0000",
               "Week 4" = "#990000")
  ) +
  theme(
    plot.title = element_text(size = 18, face = "bold"),
    plot.subtitle = element_text(size = 14),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
